Distributed Real-time Trajectory Replanning for Robust Motion Execution

### 2018-05-23 paper/paper.tex

\usetikzlibrary{arrows, arrows.meta, fit, positioning, quotes,
                shadows, shapes.geometric, shapes.misc}
\usepackage[utf8]{inputenc}

@@

% sets as caligraphics
\newcommand{\cV}{\mathcal{V}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cO}{\mathcal{O}}

% misc
\newcommand{\R}{\mathbb{R}} % real numbers

@@

\begin{abstract}
We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including newly appearing obstacles, robots breaking down, or external disturbances.
Robots do not communicate with each other and only sense other robots' positions and the obstacles around them.
At the low-level, we use buffered Voronoi cells as multi-robot collision avoidance strategy.
At the high-level we use a hybrid planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
The discrete planner helps to avoid local minima effectively, adjusts the planning horizon, and provides good initial guesses for the optimization stage.
Trajectory optimization uses a quadratic programming formulation, where all safety-critical parts are formulated as hard constraints.
We demonstrate our approach in simulation and on real robots, showing that it can operate in real-time.
%\keywords{trajectory planning, collision avoidance, multi-robot systems}
\end{abstract}

\section{Introduction}
Motion planning for multi-robot systems is widely used and in particular important in cases where many robots have to interact with each other in confined spaces, potentially with many obstacles around.
Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives like total energy used~\cite{crazyplanning-ieeetro}.
All such solutions assume that the resulting trajectories can be executed approximately perfectly, which is not true for teams of hundreds of robots that have to operate persistently.

We propose robust motion execution as a framework that takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of some robots, newly appearing obstacles, robots breaking down, or external disturbances.
Consider the example in Fig.~\ref{fig:swap2}, where two robots are tasked with swapping their positions.
The pre-planned trajectories are collision-free, but neither considers the new obstacle nor that the fact that blue robot does not start at its correct location.
Robust motion execution can be used to successfully swap positions, while staying as close as possible to the pre-planned trajectories.
Our framework is fully distributed and requires no communication; the robots only need to know their own trajectories and need to be able to sense their neighbors' positions and the obstacles around them.

\begin{figure}
%\centering
%\subfloat[Initial configuration and pre-planned trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_initial.pdf}
%\label{fig:swap2:initial}
%}
\hfill
%\subfloat[Final configuration and executed trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_final.pdf}
%\label{fig:swap2:final}
%}
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_initial.pdf}
%\caption{Initial configuration.}
%\label{fig:swap2:initial}
%\end{subfigure} \hfill
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_final.pdf}
%\caption{Final configuration and executed trajectories.}
%\label{fig:swap2:final}
%\end{subfigure}
\caption{Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines; (a)).
The initial plans were created without knowledge of the obstacle (gray) and the blue robot does not start at its planned start position.
Our approach computes smooth trajectories in real-time, avoiding the new obstacle and other robots while staying close to the pre-planned trajectory (b).
}
\label{fig:swap2}
\end{figure}

Robust motion execution is an extension of cooperative collision avoidance where the objective is to stay close to the originally planned trajectories as much as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (see Section~\ref{sec:relatedWork}).
Our method is based on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
At the high-level we employ a novel combination of trajectory optimization and discrete search-based planning with a dynamic receding horizon approach.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization takes the dynamics of real physical robots into account.

@@

\section{Problem Formulation} \label{problemFormulation}
% assumptions: circular robots; robots follow the same rules; static (or slow) obstacles
% input: original curves; positions of peers; dynamic limits; environment (at least able to sense); dt; curve_count; T
% output: at each dt: new trajectory such that there is no collision (guaranteed)
% issues: no live-lock guarantee

We consider a group of $m$ robots and each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory of $i^{th}$ robot where } t\in[0,T_i],\\
    %ct&:\text{ current global time},\\
    %\delta t&:\text{ replanning period},\\
    %\tau&: \text{time horizon},\\ 
    c&:\text{ derivative up to which smoothness is required},\\
    %\cO&:\text{ free space representation of the environment},\\
    %\{\vp_i\}&:\text{ set of positions of all robots},\\
    R_i(\vp)&:\text{ physical extent of robot $i$ at position $\vp$, and}\\
    \gamma_j&: \text{ dynamic limit of the robot for $j^{th}$ derivation degree}.%\\
    %&\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
\end{align*}

At time $t$, each robot $i$ can sense the positions $\{\vp_1(t),\ldots,\vp_m(t)\}$ of its neighbors as well as the current occupied space $\cO(t)$ around it.
We assume that $\cO(t)$ is a set of $\uptheta$ convex obstacles, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap}.
Robots cannot communicate with each other and are unaware of the other robots' trajectories.
%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
Each robot $i$ needs to execute a trajectory $\vf_i(t)$ where $\vf_i(t)$ is a solution to the following optimization problem:
\begin{align}
\begin{split}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i}{dt^j}(0)\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision free, and}\\ 
    &\left\|\frac{d^j \vf_i(t)}{dt^j}\right\| \leq \gamma_j\text{ for all desired $j$s},\\
    \text{where } & t\in [0,T_i].
\end{split}
\label{eq:problem:opt}
\end{align}

We approximately solve this problem iteratively using a dynamic receding horizon approach.
At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to period $\delta t$.
%We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.

@@

% \begin{align*}
%     \text{Given,}\ \ \ \ \ &\\
%     \vo^i(t')&:\text{ original trajectory of robot $i$},\\
%     ct&:\text{ current global time},\\
%     \delta t&:\text{ replanning period},\\
%     \tau&: \text{time horizon},\\ 
%     c&:\text{ maximum continuity between pieces},\\
%     \cO&:\text{ free space representation of the environment},\\
%     \{\vp_i\}&:\text{ set of positions of all robots},\\
%     \gamma&: \text{ dynamic limits of robots in any derivation degree},\\
%     &\ \ \ \ \gamma_j \text{ being the limit for $j^{th}$ derivation degree}\\
%     \text{find a new}&\text{ trajectory $\vf^{i,K}(t)$ such that},\\
%     \vf^{i,K}(t)&\text{ is}\text{ continuous up to degree $c$ for }t\in [0,\tau],\\
%     \frac{d^j\vf^{i,K}}{dt^j}(0) &= \frac{d^j\vf^{i,K-1}}{dt^j}(\delta t)\text{ for } j\in\{0,1,...,c\}\\
%     \vf^{i,K}(t)&\text{ is collision free for $t\in [0,\delta t]$},\\
%     \vf^{i,K}(t)&\text{ tracks $\vo^i(t')$ as close as possible for $t\in[0,\tau]$ or equivalently $t'\in[ct, ct+\tau]$ }, \text{and}\\
%     \left\|\frac{d^j \vf^{i,K}(t)}{dt^j}\right\| &\leq \gamma_j\text{ for } t\in [0,\tau],\\
% \end{align*}

@@

We now introduce important mathematical concepts and notations we use.

\subsection{Buffered Voronoi Cells} \label{bufferedVoronoi}
Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_1,r_2,...r_m \in \R$, the buffered Voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
\begin{align}
    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_i\leq 0 \right\} \label{voronoi_cell_definition}
\end{align}
where $\|\vp\|$ is the L2-norm of vector $\vp$.

The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ that is bounded by hyperplane $H_i^j$ that separates point $\vp_i$ from $\vp_j$ with normal $\valpha_i^j$ and distance along normal $\beta_i^j$ where $\valpha_i^j\in \R^n$ and $\beta_i^j\in \R$ such that
\begin{equation}
    \valpha_i^j = \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|} \text{ and }
    \beta_i^j = \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i.
    \label{voronoiAlphaBeta}
\end{equation}
% \begin{align}
%     \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
%     \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_i. \label{voronoiBeta}
% \end{align}

% The set of all buffered Voronoi cells is called the buffered Voronoi decomposition of the space.
For a given buffered Voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside at most one of the buffered Voronoi cells.
We use this property in order to avoid robot-to-robot collisions.

@@

Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of hyperplanes $H_i^j$ in $O(m)$ time.

\subsection{B\'ezier Curves} \label{bezierCurves}
A degree $d$ B\'ezier curve $\vf(t)$ parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
\begin{align}
    \vf(t; T) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T.
\end{align}

The curve starts at $\vP_0$ and ends at $\vP_d$, however does not interpolate other control points.
A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein}.
%This is called the \emph{convex hull property of B\'ezier curves}.
We use this property to avoid robot-to-obstacle collisions.

We use splines as trajectories where each piece is a B\'ezier curve. Given a trajectory $\vf^{K}_i(t)$ for robot $i$ with $l$ pieces and duration $T^{K}_i$ at iteration $K$, $T^{K}_{i,j}$ denotes the duration of the $j^{th}$ piece where $j \in \{1,2,\ldots,l\}$. $\vf^{K}_{i,j}(t)$ denotes the $j^{th}$ piece of the trajectory with implicit duration parameter $T^K_{i,j}$ where $t\in[0, T^{K}_{i,j}]$. $\vP^{K}_{i,j,\rho}$ denotes the $\rho^{th}$ control point of the $j^{th}$ piece where $\rho \in \{0,1,\ldots,d\}$.

@@

\subsection{Trajectory Optimization using Quadratic Programming} \label{trajectoryOptimization}
A part of our replanning approach utilizes \emph{quadratic programming} (QP) for trajectory optimization.
The decision variables $\vx$ are all B\'ezier curve control points concatenated.
The overall structure of our quadratic optimization problem is as follows:
\begin{align}
\begin{split}
    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^T\vg\\
    \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA.
    % &\vlb \leq \vx \leq \vub
\end{split}
\end{align}
%, while bounds on variables are represented with vectors the $\vlb$ and the $\vub$.

@@

There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector for a specified derivative. This translates to $n$ linear constraints on control points, $n$ being the dimension we are working in.
A continuity constraint between curve $j$ and curve $j+1$ requires the end of curve $j$ to be equal to the beginning of curve $j+1$ at any order of differentiation.
We take the vector difference of those values and require it to be equal to $\vzero$. This translates to $n$ linear constraints on control points.
A hyperspace constraint requires all control points of a curve to be on a specific side of a hyperplane. If a curve has $d+1$ control points, this translates to $d+1$ constraints on control points. All 3 types of constraints are linear in control points, and the exact construction is discussed in a previous work~\cite{crazyplanning-ieeetro}.

@@

%\subsection{Approach Overview}
Replanning is done at a fixed period of $\delta t$ and at each iteration $K$ we compute a trajectory $f^K_i(t)$.
The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.
In the following, we assume that the robots are spherical with a uniform radius $r_s$.
%The trajectory $f^K_i(t)$ is safe to execute at least up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.

We execute the following three major components iteratively: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot, see Fig.~\ref{fig:flowchart}.
%In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
%If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth.
%We use this discrete path as an initial guess in trajectory optimization.
%If discrete planning is not required, we use the control points of the previous plan as the initial guess.

@@

%At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c^{th}$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration. We execute this trajectory for a period of $\delta t$ and replan for the next iteration.

@@

In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered Voronoi cell $\cV_i(\psi)$.
We also assume that we have a current representation of the occupied space ($\cO(\psi)$), which can be achieved in practice by using LIDAR or RGB-D sensors.

>>>>

\usepackage{xcolor}
\newcommand{\Nora}[1] {\textbf{\textcolor{red}{#1}}}

\usetikzlibrary{arrows, arrows.meta, fit, positioning, quotes,shadows, shapes.geometric, shapes.misc}
\usepackage[utf8]{inputenc}

@@

% sets as caligraphics
\newcommand{\cV}{\mathcal{V}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cO}{\mathcal{O}}
\newcommand{\cH}{\mathcal{H}}

% misc
\newcommand{\R}{\mathbb{R}} % real numbers
\renewcommand{\th}{^{\text{th}}}

@@

\begin{abstract}
We propose a method for robust motion execution that can be applied to a wide range  of  trajectory execution tasks. 
It takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including newly appearing obstacles, robots breaking down, or external disturbances.
Robots do not communicate with each other and only sense other robots' positions and the obstacles around them.
At the low-level, we use buffered Voronoi cells as multi-robot collision avoidance strategy.
At the high-level we use a hybrid planning strategy employing both discrete planning and trajectory optimization with a dynamic receding horizon approach.
The discrete planner helps to avoid local minima effectively, adjusts the planning horizon, and provides good initial guesses for the optimization stage.
Trajectory optimization uses a quadratic programming formulation, where all safety-critical parts are formulated as hard constraints.
We demonstrate our approach in simulation and on real robots, showing that it can operate in real-time.
%\keywords{trajectory planning, collision avoidance, multi-robot systems}
\end{abstract}

\section{Introduction}
Motion planning for multi-robot systems is widely used and in particular important in cases where many robots must interact with each other in confined spaces, potentially with many obstacles around.
Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives like total energy used~\cite{crazyplanning-ieeetro}.
However, all such solutions assume that the resulting trajectories can be executed nearly perfectly, which is an unrealistic assumption for teams of hundreds of robots that must operate persistently.%, as is true in these scenarios.

We propose a method for robust motion execution that can be applied to wide range of trajectory execution tasks. It takes pre-planned trajectories as input and compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or other external disturbances.
Consider the example in Fig.~\ref{fig:swap2}(a), where two robots have to swap their positions.
Although the pre-planned trajectories are collision-free, they do not consider the new obstacle and the blue robot does not start at its correct location.
Robust motion execution can be used to successfully swap positions, while staying as close as possible to the pre-planned trajectories, as in Fig.~\ref{fig:swap2}(b).
Our method is fully distributed and requires no communication. The robots only need to know their own trajectories and be able to sense their neighbors' positions and the obstacles around them.

\begin{figure}
%\centering
%\subfloat[Initial configuration and pre-planned trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_initial.pdf}
%\label{fig:swap2:initial}
%}
\hfill
%\subfloat[Final configuration and executed trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_final.pdf}
%\label{fig:swap2:final}
%}
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_initial.pdf}
%\caption{Initial configuration.}
%\label{fig:swap2:initial}
%\end{subfigure} \hfill
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_final.pdf}
%\caption{Final configuration and executed trajectories.}
%\label{fig:swap2:final}
%\end{subfigure}
\caption{Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines; (a)).
The initial plans were created without the knowledge of the obstacle (gray) and the blue robot does not start at its planned initial position.
Our approach computes smooth trajectories in real-time, avoiding both the new obstacle and other robots while staying close to the pre-planned trajectory (b).
}
\label{fig:swap2}
\end{figure}

Robust motion execution is an extension of cooperative collision avoidance where the objective is to stay as close to the originally planned trajectories as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (we discuss these in more detail in Section~\ref{sec:relatedWork}).
Our method relies on the \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
We employ a novel combination of trajectory optimization and discrete search-based planning using a dynamic receding horizon approach.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization generates smooth trajectories that are collision-free.

We show in simulations that our method avoids collisions and deadlocks more successfully compared to ORCA~\cite{orca}.
Furthermore, we implement and test our approach on a team of six differential drive robots with several dynamic environmental changes.

@@

% \begin{tabular}{l||l}
% \hline % global
% $m$ & number of robots\\
% $n$ & problem dimension\\
% $c$ & order of derivative up to which smoothness is required \\
% $\gamma_k$ & dynamic limit of each robot for the $k\th$ derivative of its trajectory\\
% %$\Gamma_k$ & \\
% %$r_s$ & radius\\
% $R(\vp), r_s$ & space that robot occupies at position $\vp$ (sphere with radius $r_s$)\\
% $\psi$ & current time\\
% $\uptheta, \uptheta'$ & number of static obstacles\\
% \hline % per robot
% $\vo_i(t), t\in[0, T_i]$     &  original trajectory of robot $i$\\
% $\vp_i(t)$ & position of robot $i$ at time $t$\\
% $\cO_i$ & obstacles\\
% %$\vf_i(t)$ & \\
% $\cV_i$ & voronoi cell\\
% $\cS_i^j$ & \\
% $\cH_i^j, \valpha_i^j, \beta_i^j$ & hyperplane robot-robot\\
% $M_j^b$ & hyperplane robot-obstacle\\
% %$H$, $A$, $lbA$, $ubA$, $g$ & QP\\
% $K$ & iteration\\
% \hline % algorithm
% $l$ & pieces\\
% $d$ & degree\\
% $\lambda_i, \theta_j$ & QP\\
% $\tau, \tau'$ & \\
% $\delta t$ & \\
% $\vf^{K}_i(t)$ & duration $T^{K}_i$ \\
% $\vf^{K}_{i,j}(t), t\in[0, T^{K}_{i,j}]$ & $j\th$ piece\\
% $\vP^{K}_{i,j,\rho}$ & denotes the $\rho\th$ control point\\
% \end{tabular}

\section{Problem Formulation} \label{problemFormulation}
% assumptions: circular robots; robots follow the same rules; static (or slow) obstacles
% input: original curves; positions of peers; dynamic limits; environment (at least able to sense); dt; curve_count; T
% output: at each dt: new trajectory such that there is no collision (guaranteed)
% issues: no live-lock guarantee
The general problem we would like to solve can be formulated as follows. 
Consider a group of $m$ robots. Each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory of $i\th$ robot where time } t\in[0,T_i],\\
    %ct&:\text{ current global time},\\
    %\delta t&:\text{ replanning period},\\
    %\tau&: \text{time horizon},\\ 
    c&:\text{ order of derivative up to which smoothness is required},\\
    %\cO&:\text{ free space representation of the environment},\\
    %\{\vp_i\}&:\text{ set of positions of all robots},\\
    R(\vp)&:\text{ collision model of a robot at position $\vp$ (sphere with radius $r_s$), and}\\
    \gamma_k&: \text{ dynamic limit of the robot for the $k\th$ derivative of its trajectory}.%\\
    %&\ \ \ \ \gamma_j \text{ being the limit for $j\th$ derivation degree}\\
\end{align*}

Each robot $i$ can sense the positions $\{\vp_1,\ldots,\vp_m\}$ of its neighbors as well as the current occupied space $\cO_i$ around it.
We represent $\cO_i$ as a set of $\uptheta$ convex obstacles; our approach can accommodate for different sensing modalities, including LIDAR and RGB-D cameras.
%, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap} \Nora{What can be achieved? sensing them? or knowing them? or the representation?}.
Robots are unaware of the other robots' planned trajectories, and cannot communicate with each other.
%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
Each robot $i$ must execute a trajectory $\vf_i(t)$ where $\vf_i(t)$ is a solution to the following optimization problem:
\begin{align}
\begin{split}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i}{dt^j}(0)\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision free, and}\\ 
    &\left\|\frac{d^k \vf_i(t)}{dt^k}\right\| \leq \gamma_k\text{ for all desired $k$},\\
    \text{where } & t\in [0,T_i].
\end{split}
\label{eq:problem:opt}
\end{align}

We solve this problem approximately, using a dynamic receding horizon approach iteratively.
At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to period $\delta t$.
%We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.

@@

% \begin{align*}
%     \text{Given,}\ \ \ \ \ &\\
%     \vo^i(t')&:\text{ original trajectory of robot $i$},\\
%     ct&:\text{ current global time},\\
%     \delta t&:\text{ replanning period},\\
%     \tau&: \text{time horizon},\\ 
%     c&:\text{ maximum continuity between pieces},\\
%     \cO&:\text{ free space representation of the environment},\\
%     \{\vp_i\}&:\text{ set of positions of all robots},\\
%     \gamma&: \text{ dynamic limits of robots in any derivation degree},\\
%     &\ \ \ \ \gamma_j \text{ being the limit for $j\th$ derivation degree}\\
%     \text{find a new}&\text{ trajectory $\vf^{i,K}(t)$ such that},\\
%     \vf^{i,K}(t)&\text{ is}\text{ continuous up to degree $c$ for }t\in [0,\tau],\\
%     \frac{d^j\vf^{i,K}}{dt^j}(0) &= \frac{d^j\vf^{i,K-1}}{dt^j}(\delta t)\text{ for } j\in\{0,1,...,c\}\\
%     \vf^{i,K}(t)&\text{ is collision free for $t\in [0,\delta t]$},\\
%     \vf^{i,K}(t)&\text{ tracks $\vo^i(t')$ as close as possible for $t\in[0,\tau]$ or equivalently $t'\in[ct, ct+\tau]$ }, \text{and}\\
%     \left\|\frac{d^j \vf^{i,K}(t)}{dt^j}\right\| &\leq \gamma_j\text{ for } t\in [0,\tau],\\
% \end{align*}

@@

This section introduces important mathematical concepts and notation that will be used throughout the paper.

\subsection{Buffered Voronoi Cell} \label{bufferedVoronoi}
Given a set of $m$ robots with positions $\vp_1,\vp_2,\ldots,\vp_m \in \R^n$ and radii $r_s \in \R$, the buffered Voronoi cell $\cV_i$ of robot $i$ is defined as~\cite{bufferedVoronoiCells}:
\begin{align}
    \cV_i &= \left\{\vp : \forall_{j\neq i} \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \vp - \frac{\vp_j-\vp_i}{\|\vp_j-\vp_i\|}\cdot \frac{\vp_j+\vp_i}{2} + r_s\leq 0 \right\}, \label{voronoi_cell_definition}
\end{align}
where $\|\vp\|$ is the L2-norm of the vector $\vp$.

The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ bounded by hyperplane $\cH_i^j$ that separates point $\vp_i$ from $\vp_j$. $\cH_i^j$ has normal $\valpha_i^j \in \R^n$ and distance $\beta_i^j\in \R$ along $\valpha_i^j$ such that
\begin{equation}
    \valpha_i^j = \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|} \text{ and }
    \beta_i^j = \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_s.
    \label{voronoiAlphaBeta}
\end{equation}
% \begin{align}
%     \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
%     \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_s. \label{voronoiBeta}
% \end{align}

% The set of all buffered Voronoi cells is called the buffered Voronoi decomposition of the space.
For a given buffered Voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside of at most one of the buffered Voronoi cells.
We use this property in order to avoid robot-to-robot collisions.

@@

Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of the hyperplanes $\cH_i^j$ in $O(m)$ time.

\subsection{B\'ezier Curve} \label{bezierCurves}
A degree $d$ B\'ezier curve $\vf(t)$ implicitly parametrized by duration $T$ is defined by $d+1$ control points $\vP_0, \vP_1, ..., \vP_d \in \R^n$ such that
\begin{align}
    \vf(t) = \sum_{i=0}^d \vP_i {d\choose i}\left(\frac{t}{T}\right)^i\left(1-\frac{t}{T}\right)^{d-i},\hskip .5cm 0\leq t \leq T.
\end{align}

The curve starts at $\vP_0$ and ends at $\vP_d$, however does not interpolate other control points.
A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein};
%This is called the \emph{convex hull property of B\'ezier curves}.
we leverage this property to avoid robot-to-obstacle collisions.

We use splines as trajectories where each piece is a B\'ezier curve. Given a trajectory $\vf^{K}_i(t)$ for robot $i$ with $l$ pieces and duration $T^{K}_i$ at iteration $K$, $T^{K}_{i,j}$ denotes the duration of the $j\th$ piece where $j \in \{1,2,\ldots,l\}$. $\vf^{K}_{i,j}(t)$ denotes the $j\th$ piece of the trajectory with implicit duration parameter $T^K_{i,j}$ where $t\in[0, T^{K}_{i,j}]$. $\vP^{K}_{i,j,\rho}$ denotes the $\rho\th$ control point of the $j\th$ piece where $\rho \in \{0,1,\ldots,d\}$.

@@

\subsection{Trajectory Optimization using Quadratic Programming} \label{trajectoryOptimization}
Our replanning approach utilizes \emph{quadratic programming} (QP) for trajectory optimization.
The decision variables $\vx$ are the concatenated B\'ezier curve control points.
The overall structure of our quadratic optimization problem is as follows:
\begin{align}
\begin{split}
    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^T\vg\\
    \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA.
    % &\vlb \leq \vx \leq \vub
\end{split}
\end{align}
%, while bounds on variables are represented with vectors the $\vlb$ and the $\vub$.

@@

There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.
An initial point constraint on a B\'ezier curve requires the initial point of the curve to be equal to a given vector for a specified derivative. This translates to $n$ linear constraints on control points, $n$ being the dimension we are working in.
A continuity constraint between curve $j$ and curve $j+1$ requires the end of curve $j$ to be equal to the beginning of curve $j+1$ at any order of differentiation.
We take the vector difference of those values and require it to be equal to $\vzero$. This translates to $n$ linear constraints on control points.
A hyperspace constraint requires all control points of a curve to be on a specific side of a hyperplane. If a curve has $d+1$ control points, this translates to $d+1$ constraints on control points. All 3 types of constraints are linear in control points. The construction is discussed in a previous work~\cite{crazyplanning-ieeetro}.

@@

%\subsection{Approach Overview}
Replanning is done at a fixed period of $\delta t$.
In each iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions to compute the buffered Voronoi cell $\cV_i$, update our current representation of the occupied space ($\cO_i$), and compute a trajectory $f^K_i(t)$.
The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.

% In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered Voronoi cell $\cV_i$.
% We also assume that we have a current representation of the occupied space ($\cO_i$). Even if we use the complete occupation map in our examples, our method also works for local maps which can be constructed in practice by using LIDAR or RGB-D sensors.

%The trajectory $f^K_i(t)$ is safe to execute at least up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.

We execute the following three major components iteratively: \emph{discrete planning} that is used to efficiently plan around new obstacles, \emph{trajectory optimization} to generate smooth and collision-free trajectories, and \emph{temporal rescaling} to enforce the dynamic limits of the robot (see Fig.~\ref{fig:flowchart}).

%In the beginning of each iteration, we check several conditions to decide if discrete planning is required.
%If discrete planning is required, we execute a discrete search that results in a discrete path that is collision free but not smooth.
%We use this discrete path as an initial guess in trajectory optimization.
%If discrete planning is not required, we use the control points of the previous plan as the initial guess.

@@

At the end of each iteration, each robot has its trajectory $\vf^{K}_i(t)$ that is guaranteed to be collision-free up to time $\delta t$, is continuous up to the $c\th$ derivative, obeys the dynamic limits of the robot, tries to stay close to the original trajectory, and is a good starting point for the next iteration. We execute this trajectory for a period of $\delta t$ and replan for the next iteration.

@@

Robot $i$ executes discrete planning if any of the following conditions are true:
\begin{enumerate}
    \item The original trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [\psi,\psi+\tau] : R(\vo_i(t)) \cap \cO_i \neq \emptyset$,
    \item The first piece of the previously planned trajectory is outside the robot's buffered Voronoi cell, i.e., $\exists t\in [0, T^{K-1}_{i,1}] : \vf^{K-1}_{i,1}(t) \not\in \cV_i$, or
    \item The previously planned trajectory is not collision-free for the desired time horizon $\tau$, i.e., $\exists t\in [0,\tau] :  R(\vf^{K-1}_i(t)) \cap \cO_i \neq \emptyset$.
\end{enumerate}
The first condition handles cases where previously unknown obstacles block the pre-planned path of a robot, the second condition handles cases where previously unknown robots appear and cases where robots are close and moving towards each other, and the third condition handles dynamic obstacles and numerical issues that resulted in a trajectory with collisions in the previous iteration. The main reason of these numerical issues is explained in Section~\ref{simulationSection}.
